IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-18 paper/retrofit.tex
Crossing sout

\begin{itemize}
    \item First-class labels, with label values $l$ as well as operations for computing on
labels (|canFlowTo|, |lub| and |glb|).
    \item Operations for inspecting (\textbf{getLabel}) and modifying
    (\textbf{setLabel}) the current label of the task (a task can only increase its label).
    \item Operations for non-blocking inter-task communication (\textbf{send}
    and \textbf{recv}), which interact with the global store of per-task
    message queues |iS|.
%%     Labels are associated with message at the time of
%%     the send; the label on a message must always be at least as sensitive as that
%%     of the sending thread, since, conceptually, once a message is put on a
%%     message queue it is no longer protected by the current label, rather it is
%%     protected by the message label.
%%     Dually, when reading a message with |recv| the current label of the
%%     receiver must be at least as high as the message label.
    \item A sandboxing operation used to spawn new isolated tasks. In
    concurrent settings |fork| corresponds to a fork-like primitive,
    whereas in a
    sequential setting, it more closely resembles

    \sout{the LIO
    |toLabeled|~\cite{lio} and Breeze
    bracket~\cite{Hritcu:2013:YIB:2497621.2498098} constructs.}
    \Red{
      computations which might temporarely raise the current
      floating-label~\cite{lio,Hritcu:2013:YIB:2497621.2498098}.
    }
\end{itemize}

>>>>

\begin{itemize}
    \item First-class labels, with label values $l$ as well as operations for computing on
labels (|canFlowTo|, |lub| and |glb|).
    \item Operations for inspecting (\textbf{getLabel}) and modifying
    (\textbf{setLabel}) the current label of the task (a task can only increase its label).
    \item Operations for non-blocking inter-task communication (\textbf{send}
    and \textbf{recv}), which interact with the global store of per-task
    message queues |iS|.
%%     Labels are associated with message at the time of
%%     the send; the label on a message must always be at least as sensitive as that
%%     of the sending thread, since, conceptually, once a message is put on a
%%     message queue it is no longer protected by the current label, rather it is
%%     protected by the message label.
%%     Dually, when reading a message with |recv| the current label of the
%%     receiver must be at least as high as the message label.
    \item A sandboxing operation used to spawn new isolated tasks. In
    concurrent settings |fork| corresponds to a fork-like primitive,
    whereas in a
    sequential setting, it more closely resembles
    computations which might temporarely raise the current
    floating-label~\cite{lio,Hritcu:2013:YIB:2497621.2498098}.

\end{itemize}
